---
title: "Demonstration of how to build a credit risk scorecard in R"
author: "David Mortimer"
date: "21 July 2021"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    number_sections: true
    self_contained: yes
    css: corp-styles.css
    highlight: pygments
---


<div class="watermark">DRAFT</div>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE, eval = TRUE)
```

# Executive Summary

R Markdown is a great way to turn your analysis into a portable, reproducible document - such as pdf or html. This document demonstrates how to incorporate Healths corporate style guide into Rmarkdown documents.

```{r results = 'asis', message=F, warning=F}
#library(openxlsx)
library(tidyverse)
library(stringr)
library(scales)    # to show scale in percent
library(ggseas)    # for seasonal adjustment on the fly
library(forcats)   # for munging factors
library(extrafont) # in case running on windows
library(stringi)   # for generating pseudo lating lorem ipsum text
library(here)
library(lubridate)
library(zoo)
library(scales)
library(skimr)
library(scorecard)
library(knitr)

source(here('corp-palette.R'))
#cat(stri_rand_lipsum(1))

hmeq <- read_csv(here("data/hmeq.csv"))
```
## Data Description

The classic HMEQ dataset - containing data relating to Home Equity Loan performance.

## Data profiling

The skimr package provides a nice way to quickly profile the input training dataset.

```{r pressure, echo=FALSE}
skim(hmeq)
```

## Univariate Analysis

The purpose of univariate analysis is to:

1. Examine the relationship of each individual variable to the target (ie. loan default)
2. Evaluate the input variables for candidates to use in model training
3. Screen out un-predictive variables

The univariate analysis is performed by first binning each variable into discrete categories - sometimes called discretization in machine learning.

Each variable is binned into homogeneous groups that optimise the relationship to the target.

```{r binning, echo=FALSE}
bins <- woebin(hmeq , "BAD")

iv <- iv(hmeq , "BAD")

```

**Information Value (IV) summary**

```{r print_tab, echo=FALSE}

kable(iv)
```

## Variable Selection/Screening


## Scorecard Fitting/Scaling
